Quantitative Auditing of AI Fairness with Differentially Private Synthetic Data

### 2024-12-18 paper/paper.tex
minor

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
Ensuring fairness in AI systems is crucial, but auditing these systems often requires sensitive data, which raises security and privacy concerns. To address this, we introduce a framework that utilizes differentially private synthetic data for fairness evaluations. This approach allows auditors to assess AI systems without exposing sensitive information. Through experiments on datasets like Adult, COMPAS, and Diabetes, we compare fairness metrics of synthetic and real data. Our results ... (to be continued)
\end{abstract}

@@

>>>>

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
Auditing AI systems often requires sensitive data, raising security and privacy concerns. To address this, we propose a framework that leverages differentially private synthetic data for fairness evaluations. This approach enables auditors to assess AI systems without exposing sensitive information. Through experiments on real datasets like Adult, COMPAS, and Diabetes, we compare fairness metrics of synthetic and real data. Our results show that synthetic data accurately reflect the fairness properties of real data to a reasonable extent.
\end{abstract}

@@

Auditing AI systems with real data can be dangerous. We proffer a new approach that leverages differentially private synthetic data. The proposed framework under such privacy guarantees offers a refuge from the vulnerabilities of using real data.

Despite the fact that some measures' definitions betray the inherent imperfection of synthetic data, the metrics results remain generally consistent with the original data. Empirical trials across multiple real-world datasets and real-world models reveal that synthetic data derived from real data sufficiently maintains the fairness properties to serve as instruments of audit.

Auditors are, thus, in our new framework, equipped with a new tool that tempers risk at the cost of nuance. Synthetic data, imperfect as it is, emerges as a pragmatic ally, preserving enough fairness properties for auditing utility without sacrificing the sanctuary of privacy.
